R for Clinical Study Reports and Submission

### 2022-02-28 slides/china-r.Rmd
Deploying to gh-pages from @ elong0527/r4csr@4ca950c2f5252a5bdd26e7e5a7cd0318dadac192 🚀

- Clinical study report is a key deliverable for clinical trials to regulatory agencies. (e.g., FDA, CFDA)
  + [ICH E3 Structure and Content of Clinical Study Reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf)

- We try to fill in gaps to streamline workflow using R:
  + To develop, validate, deliver analysis results.
  + To submit analysis results to regulatory agencies in [eCTD format](https://en.wikipedia.org/wiki/Electronic_common_technical_document).

- Focus on table, listing, figure (TLFs) delivered in RTF/Microsoft Word format
  + In the pharmaceutical industry, RTF/Microsoft Word play a central role in preparing clinical study reports.
  + Different organization can have different table standards

@@

- Contact us for R developer or Methodology Research Positions:
  + Yilong Zhang: <https://elong0527.github.io/>
  + Nan Xiao: <https://nanx.me/>
  + Keaven Anderson: <https://www.linkedin.com/in/keaven-anderson-09aa7538/>

- Multiple open positions (statisticians/programmers) in China, EU, and US
  + US: <https://jobs.merck.com/bards>
  + China/EU: <https://jobs.msd.com/cn/zh>

>>>>

- Clinical study report is a key deliverable for clinical trials to regulatory agencies. (e.g., FDA, CFDA)
  - [ICH E3 Structure and Content of Clinical Study Reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf)

- We try to fill in gaps to streamline workflow using R:
  - To develop, validate, deliver analysis results.
  - To submit analysis results to regulatory agencies in [eCTD format](https://en.wikipedia.org/wiki/Electronic_common_technical_document).

- Focus on table, listing, figure (TLFs) delivered in RTF/Microsoft Word format
  - In the pharmaceutical industry, RTF/Microsoft Word play a central role in preparing clinical study reports.
  - Different organization can have different table standards

@@

- Contact us for R developer or Methodology Research Positions:
  - Yilong Zhang: <https://elong0527.github.io/>
  - Nan Xiao: <https://nanx.me/>
  - Keaven Anderson: <https://www.linkedin.com/in/keaven-anderson-09aa7538/>

- Multiple open positions (statisticians/programmers) in China, EU, and US
  - US: <https://jobs.merck.com/bards>
  - China/EU: <https://jobs.msd.com/cn/zh>

### 2022-02-28 slides/workshop-slides.Rmd
Deploying to gh-pages from @ elong0527/r4csr@4ca950c2f5252a5bdd26e7e5a7cd0318dadac192 🚀

```{r, message=FALSE}
library(dplyr)
library(tidyr)
library(r2rtf)
```

@@

- Delivering TLFs in CSR (Yilong Zhang)
  + Session 1 (45 min)
  + Break and/or Exercise (20 min)
  + Session 2 (45 min)
  + Break (10 min)
- Clinical trial project (Nan Xiao)
  + Session 3 (30 min)
  + Break (10 min)
- eCTD submission package (Nan Xiao)
  + Session 4 (40 min)
  + Q&A (10 min)

@@

## Training Objective

@@

- Team members from Merck & Co.
  + [We are hiring!](https://jobs.merck.com/bards)
  + Contact us if interested.

- [Contributors](https://r4csr.org/) of the training materials.
  + Please consider submitting issues or PR in the repo.

- [R Consortium](https://www.r-consortium.org/projects/isc-working-groups)
  + R validation hub
  + Submission working group
  + R Tables for Regulatory Submission (RTRS) working group
  + Please consider to join and contribute to a working group.

- [ASA Princeton-Trenton Chapter](https://community.amstat.org/princetontrenton/home)
  + Please consider to be a member of our chapter.

@@

- Training Material: <https://r4csr.org/>
- Demo project:
  + Analysis project: <https://github.com/elong0527/esubdemo>
  + eCTD submission package: <https://github.com/elong0527/ectddemo>
- R Consortium FDA submission pilot:
  + <https://github.com/RConsortium/submissions-pilot1>

- During the workshop, we will use `esubdemo` project.
  + `esubdemo` is shared in RStudio Cloud (<https://rstudio.cloud/>)
  + Project link will be shared in chat
  + Post questions in group chat.

@@

## ICH E3 Guidance

@@

# r2rtf Introduction

@@

- provide simple "verb" functions that correspond to each component of a table,
  to help you translate a data frame to a table in RTF format.
- enable pipes (`%>%`).
- only focus on the **table format**.
  + Data manipulation and analysis shall be handled by other R packages. (e.g. `tidyverse`)

@@

## Minimal Example

`r2rtf` is designed to enable pipes (`%>%`)

@@

## Package Overview

@@

## Simple Example - Adverse Events

`r2rtf` only focus on **table format**.
Data manipulation and analysis shall be handled by other R packages. (e.g. `tidyverse`)

@@

## Function Summary

@@

## Function Illustration

```{r, out.width="80%", echo=FALSE, fig.align="center"}
knitr::include_graphics("function-summary.png")
```

# Break and/or Exercise (20 min)

# CSR Examples

## Disposition Table

@@

## Analysis Population

@@

## Baseline Characteristics

@@

## Efficacy Table

@@

## AE Summary Table

@@

## Specific AE Table

@@

# Clinical Trial Project

@@

## Folder Structure

@@

## Project Management

@@

# eCTD Submission

@@

## Submission Package

@@

## Running Environment

@@

## pkglite: Compact Package Representations

@@

## Pipe-Friendly Workflow

@@

## File Specifications + File Collections

@@

```
# Generated by pkglite: do not edit by hand
# Use pkglite::unpack() to restore the packages

>>>>

```{r, include=FALSE}
library(dplyr)
library(tidyr)
library(r2rtf)
```

@@

- Delivering TLFs in CSR (Yilong Zhang)
  - Session 1 (45 min)
  - Break and/or Exercise (20 min)
  - Session 2 (45 min)
  - Break (10 min)
- Clinical trial project (Nan Xiao)
  - Session 3 (30 min)
  - Break (10 min)
- eCTD submission package (Nan Xiao)
  - Session 4 (40 min)
  - Q&A (10 min)

@@

## Training objective

@@

- Team members from Merck & Co.
  - [We are hiring!](https://jobs.merck.com/bards)
  - Contact us if interested.

- [Contributors](https://r4csr.org/) of the training materials.
  - Please consider submitting issues or PR in the repo.

- [R Consortium](https://www.r-consortium.org/projects/isc-working-groups)
  - R validation hub
  - Submission working group
  - R Tables for Regulatory Submission (RTRS) working group
  - Please consider to join and contribute to a working group.

- [ASA Princeton-Trenton Chapter](https://community.amstat.org/princetontrenton/home)
  - Please consider to be a member of our chapter.

@@

- Training Material: <https://r4csr.org/>
- Demo project:
  - Analysis project: <https://github.com/elong0527/esubdemo>
  - eCTD submission package: <https://github.com/elong0527/ectddemo>
- R Consortium FDA submission pilot:
  - <https://github.com/RConsortium/submissions-pilot1>

- During the workshop, we will use `esubdemo` project.
  - `esubdemo` is shared in RStudio Cloud (<https://rstudio.cloud/>)
  - Project link will be shared in chat
  - Post questions in group chat.

@@

## ICH E3 guidance

@@

# r2rtf introduction

@@

- provide simple "verb" functions that correspond to each component of a table,
  to help you translate a data frame to a table in RTF format;
- enable pipes (`%>%`);
- only focus on the **table format**.
  - Data manipulation and analysis should be handled by other R packages. (e.g., `tidyverse`)

@@

## Minimal example

`r2rtf` is designed to enable pipes (`%>%`).

@@

## Package overview

@@

## Simple example: adverse events

`r2rtf` only focus on **table format**.
Data manipulation and analysis should be handled by other R packages. (e.g., `tidyverse`)

@@

## Function summary

@@

## Function illustration

```{r, out.width="100%", echo=FALSE, fig.align="center"}
knitr::include_graphics("function-summary.png")
```

# Break and/or exercise (20 min)

# CSR examples

## Disposition table

@@

## Analysis population

@@

## Baseline characteristics

@@

## Efficacy table

@@

## AE Summary table

@@

## Specific AE table

@@

# Clinical trial project

@@

## Folder structure

@@

## Project management

@@

# eCTD submission

@@

## Submission package

@@

## Running environment

@@

## pkglite: compact package representations

@@

## Pipe-friendly workflow

@@

## File specifications + file collections

@@

```text
# Generated by pkglite: do not edit by hand
# Use pkglite::unpack() to restore the packages
